On the effects of partying on next-day sports performance

### 2017-05-24 writing/draft.tex
Added a skeleton outline and some rough thoughts to Intro, and Data sections.

@@

\section{Introduction}
\section{Previous Research}
\section{Materials and Methods}
\subsection{Data}
\section{Results}
\section{Conclusions}
\section{References}

>>>>

\usepackage{hyperref}

@@

\section{Introduction}
It's not unreasonable to think that game performance can be affected 
(in part) by what takes place off the court. We are interested to see if 
teams exhibit a decline in performance the day following a game in a city 
with active nightlife. We exploit data on bookmaker spreads, the expected score 
differential between two teams after conditioning on observable performance. 
We expect a team to meet the spread half the time, since this is how bookmakers 
minimize risk on their end. We construct a model which attempts to 
estimate the causal effect of  visiting a "party-city" on subsequent day 
performance as measured by the spread. Since next-day
opponent is uncorrelated with exposure to treatment, we have identification in our variable of 
interest.

\section{Previous Research}

\section{Materials and Methods}
\subsection{Data}
\subsubsection{Lines data} We obtained data from \href{http://www.covers.com/sports/NBA/matchups?selectedDate=2011-1-01}{Covers.com}, which records the outcome of each game alongside the line set by a betting house.

\subsubsection{BLS data} We also obtained data from
\href{https://www.bls.gov/data/}{Bureau of Labor Statistics} which records the number of establishments by business type at the county-quarter level. As a 
proxy for how much night-life there is in a city, we look toward the 
number of sound recording studios, musical groups, and music publishers there 
are for a particular county-year: we simply calculate the average number of establishments across all three music categories listed above.\footnote{We caveat that since the Toronto Raptors are located in Canada, we don't have BLS data for this team.}

We then merge this in with our lines data, taking care to do so according to each season-team's last game location; we also lag our BLS data by one year.
To this data, we've created features such as 
the number of days since last game, the last game location, the travel distance, and
average age\footnote{We use $\log \textrm{\# days old}$, at the time the game is played.}. Our data range from 2010-2011 season through present, which includes part of the 2016-2017 season.

\subsubsection{Minutes data}
We also gathered minutes data from \href{http://www.espn.com/nba/scoreboard/_/date/}{ESPN}.

The minutes data also contain information on the number of free throws, field goals, and
three pointers made and attempted by each player in each game.

\subsubsection{Which cities (don't) have nightlife?}

We examine which cities have a notable nightlife, as measured by our proxy;
bottom and top five.

Los Angeles stands out, as does New York. Some runner ups include Chicago and Miami.

\subsection{Method: Defining a continuous measure of night life}

We have a free parameter: the time-window which we believe the hangover effect
to last. Suppose we only look toward games which have been played in a party
city at most 24 hours ago. We take care to ignore
teams playing in their own cities.

\subsection{Possible confounders}
What if we pick up effects of a busy play schedule?
Aside from accounting for how much rest time a team is allowed in between games,
and travel distance between games, we're also interested to get a measure of
fatigue incurred on the court.
We account for this by bringing in minutes data, and counting the number of 
times the players run back and forth on the court. This is crudely measured
by the number of changes in posession. We back out this quantity.

\section{Results}

\section{Conclusions}

\section{References}
